---
title: "main2"
author: "Yitong Hu  (yh2875)"
date: "2017/3/12"
output: html_document
---

```{r}
if(!require("EBImage")){
  source("https://bioconductor.org/biocLite.R")
  biocLite("EBImage")
}

if(!require("gbm")){
  install.packages("gbm")
}

library("EBImage")
library("gbm")
```

```{r}
dat_train<-read.csv("../data/training_data/sift_features/sift_features.csv")
dat_train<-t(dat_train)
```

### Step 1: set up controls for evaluation experiments.

In this chunk, ,we have a set of controls for the evaluation experiments. 

+ (T/F) cross-validation on the training set
+ (number) K, the number of CV folds
+ (T/F) process features for training set
+ (T/F) run evaluation on an independent test set
+ (T/F) run evaluation on an independent test set

```{r exp_setup}
run.cv=TRUE # run cross-validation on the training set
K <- 5  # number of CV folds
run.feature.train=TRUE # process features for training set
run.test=TRUE # run evaluation on an independent test set
run.feature.test=TRUE # process featur  es for test set
```

Using cross-validation or independent test set evaluation, we compare the performance of different classifiers or classifiers with different specifications. In this example, we use GBM with different `depth`. In the following chunk, we list, in a vector, setups (in this case, `depth`) corresponding to models that we will compare. In your project, you maybe comparing very different classifiers. You can assign them numerical IDs and labels specific to your project. 

```{r model_setup}
model_values <- seq(3, 11, 2)
model_labels = paste("GBM with depth =", model_values)
```


### Step 2: import training images class labels.

For the example of zip code digits, we code digit 9 as "1" and digit 7 as "0" for binary classification.

```{r train_label}
#setwd("../data/training_data")
label_train <- read.csv("../data/training_data/labels.csv")
label_train <- as.numeric(label_train[1:2000,])
```


### Step 4: Train a classification model with training images
Call the train model and test model from library. 

`train.R` and `test.R` should be wrappers for all your model training steps and your classification/prediction steps. 
+ `train.R`
  + Input: a path that points to the training set features.
  + Input: an R object of training sample labels.
  + Output: an RData file that contains trained classifiers in the forms of R objects: models/settings/links to external trained configurations.
+ `test.R`
  + Input: a path that points to the test set features.
  + Input: an R object that contains a trained classifiers.
  + Output: an R object of class label predictions on the test set. If there are multiple classifiers under evaluation, there should be multiple sets of label predictions. 
```{r loadlib}
source("../lib/train.R")
source("../lib/test.R")
```

#### Model selection with cross-validation
* Do model selection by choosing among different values of training model parameters, that is, the interaction depth for GBM in this example. 
```{r runcv, message=FALSE, warning=FALSE}

source("../lib/cross_validation.R")

if(run.cv){
  err_cv <- array(dim=c(length(model_values), 2))
  for(k in 1:length(model_values)){
    cat("k=", k, "\n")
    err_cv[k,] <- cv.function(dat_train, label_train, model_values[k], K)
  }
  save(err_cv, file="../output/err_cv.RData")
}
```

Visualize cross-validation results. 
```{r}

err_cv[,1]
model_values
```



```{r cv_vis}
library(ggplot2)
#if(run.cv){
  #load("../output/err_cv.RData")
  #pdf("../fig/cv_results.pdf", width=7, height=5)
#ggplot(data = err_cv)+  
plot(model_values, err_cv[,1])
  #points(model_values, err_cv[,1], col="blue", pch=16)
  #lines(model_values, err_cv[,1], col="blue")
  #arrows(model_values, err_cv[,1]-err_cv[,2], model_values, err_cv[,1]+err_cv[,2], 
        #length=0.1, angle=90, code=3)
  #dev.off()
#}
```


* Choose the "best"" parameter value

```{r best_model}
model_best=model_values[1]
if(run.cv){
  model_best <- model_values[which.min(err_cv[,1])]
}

par_best <- list(depth=model_best)
```
```




* Train the model with the entire training set using the selected model (model parameter) via cross-validation.




```{r final_train}
tm_train=NA
tm_train <- system.time(fit_train <- train(dat_train, label_train, par_best))
save(fit_train, file="../output/fit_train.RData")
```

### Step 5: Make prediction 
Feed the final training model with the completely holdout testing data. 
```{r test}
tm_test=NA
if(run.test){
  load(file=paste0("../output/feature_", "zip", "_", "test", ".RData"))
  load(file="../output/fit_train.RData")
  tm_test <- system.time(pred_test <- test(fit_train, dat_test))
  save(pred_test, file="../output/pred_test.RData")
}
```

### Summarize Running Time
Prediction performance matters, do does the running times for constructing features and for training the model, especially when the computation resource is limited. 
```{r running_time}
cat("Time for constructing training features=", tm_feature_train[1], "s \n")
cat("Time for constructing testing features=", tm_feature_test[1], "s \n")
cat("Time for training model=", tm_train[1], "s \n")
cat("Time for making prediction=", tm_test[1], "s \n")
```


